Estimating individual subjective values of emotion regulation strategies

### 2022-02-22 06_Paper/ER-ED/Manuscript_ERED_Stage1.Rmd
added supplement ERQ

## Pilot study: Subjective arousal in the conditions "Active viewing - neutral" and "Active viewing - negative"
ANOVA:

>>>>

## Detailed information on psychometric measures

*General psychological well-being.*

*Resilience.*

*Habitual use of reappraisal and suppression.* 
Habitual use of reappraisal and suppression was measured using the 10-item Emotion Regulation Questionnaire (ERQ)[@GrossJohn2003;@Abler2009].
The scale has items such as "I keep my emotions to myself" (ERQ-suppression) and "When I'm faced with a stressful situation, I make myself think about it in a way that helps me stay calm" (ERQ-reappraisal), which are answered on a 7-point Likert scale ranging from 1 (strongly disagree) to 7 (strongly agree), and has acceptable to high internal consistency (Cronbach’s $\alpha>.75$) [@Preece2020].

\newpage
## Pilot study: Subjective arousal in the conditions "Active viewing - neutral" and "Active viewing - negative"
ANOVA:
